Two Mode Networks and Relational Similarity

### 2023-09-07 analysis.qmd
New simrank analysis and plot

# Setup
```{r setup}
   knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
   library(cowplot)
   library(here)
   library(patchwork)
   library(dplyr)
   library(ggbump)
   library(ggplot2)
   library(ggrepel)
   library(igraph)
   library(pals)
   source(here("Functions", "TwoModeCA.R"))
   source(here("Functions", "reflections.R"))
   source(here("Functions", "ref.long.dat.R"))
```

@@

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A, k.r = 5)

@@

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- a$A.plot.ca
   c <- a$A.plot.bon
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
   dev.off() 
```

```{r Similarity and Correspondence Plot (Bonacich)}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 6, d.r = 6, d.c = 6, b.r = 4, b.c = 4)
    a <- tmCA.res$bon.sim.plot.r + theme(axis.text.x = element_blank())
    b <- tmCA.res$bon.sim.plot.c + theme(axis.text.x = element_blank())
    c <- tmCA.res$bon.corr.plot

@@

```{r Main Plot}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 6, k.c = 6, d.r = 9, d.c = 9)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmCA.res$sim.plot.r + theme(axis.text.x = element_blank())
    f <- tmCA.res$sim.plot.c + theme(axis.text.x = element_blank())
    g <- tmCA.res$corr.plot

    png(file = here("Plots", "eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off()

    png(file = here("Plots", "sim.png"), width=950, height=700)
        (e | f) / g + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```

>>>>

# Setup
```{r setup}
   knitr::opts_chunk$set(include = TRUE, 
                       echo = FALSE, 
                       warning = FALSE, 
                       message = FALSE)
   library(cowplot)
   library(here)
   library(patchwork)
   library(dplyr)
   library(factoextra)
   library(ggbump)
   library(ggcorrplot)
   library(ggplot2)
   library(ggpubr)
   library(ggrepel)
   library(igraph)
   library(pals)
   library(patchwork)
   source(here("Functions", "TwoModeCA.R"))
   source(here("Functions", "TwoModeSR.R"))
   source(here("Functions", "reflections.R"))
   source(here("Functions", "ref.long.dat.R"))
```

@@

@@

```{r CA versus Bonacich Re-ordered Affiliation Matrices}
   source(here("Functions", "TwoModeCA.R"))
   a <- TwoModeCA(A)
   b <- a$ca.A
   c <- a$bon.A
   png(file = here("Plots", "ca-v-bon-reord.png"), width=1000, height=700)
      (b | c) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
   dev.off() 
```

```{r Eigenvector Plot}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, k.r = 2, k.c = 2)
    a <- tmCA.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmCA.res$eigvec.plot.c 
    c <- tmCA.res$eigval.plot.r
    d <- tmCA.res$eigval.plot.c
    a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)

    png(file = here("Plots", "eigvec.png"), width=1000, height=600)
        (a | b) + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20))
    dev.off() 
```

```{r Similarity and Correspondence Plot (CA)}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, d.r = 4, d.c = 4, k.r = 3, k.c = 3)
    a <- tmCA.res$ca.sim.plot.r + theme(axis.text.x = element_blank())
    b <- tmCA.res$ca.sim.plot.c + theme(axis.text.x = element_blank())
    c <- tmCA.res$ca.corr.plot

    png(file = here("Plots", "ca-sim.png"), width=950, height=700)
      (a | b) / c + plot_annotation(tag_levels = "a") &
      theme(plot.tag = element_text(size = 20)) 
    dev.off() 
```

```{r Similarity and Correspondence Plot (Bonacich)}
   source(here("Functions", "TwoModeCA.R"))
    tmCA.res <- TwoModeCA(A, d.r = 4, d.c = 4, b.r = 4, b.c = 4)
    a <- tmCA.res$bon.sim.plot.r + theme(axis.text.x = element_blank())
    b <- tmCA.res$bon.sim.plot.c + theme(axis.text.x = element_blank())
    c <- tmCA.res$bon.corr.plot

@@

```{r SimRank Plot}
   source(here("Functions", "TwoModeSR.R"))
   tmSR.res <- TwoModeSR(A, C = 0.8, iter = 10)
    a <- tmSR.res$eigvec.plot.r + theme(axis.text = element_blank())
    b <- tmSR.res$eigvec.plot.c 
    c <- tmSR.res$eigval.plot.r
    d <- tmSR.res$eigval.plot.c
    #a <- a + inset_element(c, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    #b <- b + inset_element(d, left = 0.01, right = 0.4, bottom = 0.55, top = 1)
    e <- tmSR.res$A.plot
    f <- tmSR.res$corr.plot
   dat.r <- data.frame(ca = as.numeric(tmCA.res$ca.eigvec.r[,1]),
                       sr = tmSR.res$ov.r,
                       lab = rownames(A))
   dat.c <- data.frame(ca = as.numeric(tmCA.res$ca.eigvec.c[,1]),
                       sr = tmSR.res$ov.c,
                       lab = colnames(A))
   g <- ggscatter(dat.r, x = "ca", y = "sr", 
                  label = "lab", repel = TRUE, 
                  add = "reg.line", 
                  add.params = list(color = "gray80", linewidth = 0.25))
   h <- ggscatter(dat.c, x = "ca", y = "sr", 
                  label = "lab", repel = TRUE, 
                  add = "reg.line",
                  add.params = list(color = "gray80", linewidth = 0.25))
   i <- (a | b | (g / h)) + plot_layout(widths = c(2, 2, 1))
   j <- (e | f) + plot_layout(widths = c(1, 3))

   png(file = here("Plots", "sr-plot.png"), width=1000, height=1200)
       (i / j ) +
       plot_annotation(tag_levels = "a") &
       theme(plot.tag = element_text(size = 20))
    dev.off()

```{r}
```

```{r}
